Guided Proofreading of Automatic Segmentations for Connectomics

### 2016-11-15 paper/method.tex
Replace UI.
Fixes.

\begin{figure}[t]
\begin{center}
  \includegraphics[width=\linewidth]{gfx/cnn_inputs.pdf}
\end{center}
 % \vspace{-4mm}
   \caption{Example inputs for learning correct splits and split errors, as per a candidate segmentation versus the ground truth. Image, membrane probabilities, merged binary labels, and a dilated border mask provide 4-channel input patches.}
\label{fig:cnn_inputs}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
  \includegraphics[width=\linewidth]{gfx/merge_error.pdf}
\end{center}
%  \vspace{-4mm}
   \caption{Merge errors are identified by generating randomly-seeded watershed borders within a dilated label segment. Then, each border is individually rated using the split error CNN by inverting the probability score. A confident rating for a correct split most likely indicates the missing border of the merge error, and can be used to correct the labeling.\JT{Candidate to improve.}}
\label{fig:merge_error}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\linewidth]{gfx/user_interface_split.pdf}
\caption{Our guided proofreading user interface. A candidate error region is shown on the left. The user must choose between the region being a split error which needs correcting (center) or not (right). Hovering highlights the current selection with a yellow border, and a mouse click confirms the choice and advances to the next potential error.}
\label{fig:ui}
\end{figure}

>>>>

\begin{figure}[t]
\centering  
\includegraphics[width=\linewidth]{gfx/cnn_inputs.pdf}
\caption{Example inputs for learning correct splits and split errors, as per a candidate segmentation versus the ground truth. Image, membrane probabilities, merged binary labels, and a dilated border mask provide 4-channel input patches.}
\label{fig:cnn_inputs}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/merge_error.pdf}
\caption{Merge errors are identified by generating randomly-seeded watershed borders within a dilated label segment. Then, each border is individually rated using the split error CNN by inverting the probability score. A confident rating for a correct split most likely indicates the missing border of the merge error, and can be used to correct the labeling.}
\label{fig:merge_error}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\linewidth]{gfx/user_interface_split.pdf}
\caption{Our guided proofreading user interface. A candidate error region is shown on the left. The user must choose between the region being a split error which needs correcting (center) or not (right). Hovering highlights the current selection with a blue border, and a mouse click confirms the choice and advances to the next potential error.}
\label{fig:ui}
\end{figure}

### 2016-11-15 paper/results.tex
Fix typo.
Fixes.

We compare the guided proofreading and focused proofreading classifiers and report precision and recall as well as f1 scores across datasets.

\paragraph{L. Cylinder.} Evaluation was performed on previously unseen sections of mouse cortex volume of Kasthuri~\etal~\cite{kasthuri2015saturated}. We generated an unbalanced dataset of 81,184 correct and 8,780 split error patches in respect to the ground truth labeling. We then ranked each patch by using focused proofreading, guided proofreading and compared precision/recall (Table \ref{tab:prcyl}. Our method exhibits higher precision and recall for correct and error patches.

\begin{table}[h]
\caption{Classifier comparison on an unbalanced test set of the L. Cylinder volume.}%While the training of our classifier is more expensive, testing accuracy is superior. }

\small{
\begin{tabular}{l|c|c|c|c}

 & precision & recall & f1 score & \# \\ 
\textbf{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
correct & 0.93 & 0.31 & 0.47 & 81,184 \\ 
split error & 0.11 & 0.78 & 0.19 & 8,780 \\ 
\textbf{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
correct & 1.00 & 0.93 & 0.96 & 81,184 \\ 
split error & 0.61 & 0.96 & 0.74 & 8,780 \\ 
\end{tabular} 
}
\label{tab:prcyl}
\end{table}

@@

\begin{table}[h]
\caption{Classifier comparison on correct and split error patches of the AC4 subvolume.}%While the training of our classifier is more expensive, testing accuracy is superior. }

\small{
\begin{tabular}{l|c|c|c|c}

 & precision & recall & f1 score & \# \\ 
\textbf{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
correct & 0.94 & 0.69 & 0.80 & 3,488 \\ 
split error & 0.14 & 0.51 & 0.21 & 332 \\ 
\textbf{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
correct & 1.00 & 0.92 & 0.96 & 3,488 \\ 
split error & 0.54 & 0.95 & 0.69 & 332 \\ 
\end{tabular} 
}
\label{tab:prac4}
\end{table}

@@

\paragraph{Selection oracle.} Accepting and rejecting proofreading corrections with the selection oracle yields the best performance on all datasets because all detected merge and split errors are corrected as long as the segmentation is improved. Fig.~\ref{fig:ac4trails} shows slope of VI reduction using the selection oracle on the AC4 subvolume (initial median VI $0.476$, $SD=0.089$). With focused proofreading, the selection oracle reaches a median VI of $0.353$ ($SD=0.037$) after $1605$ corrections. With guided proofreading, the oracle results in a median VI of $0.342$ ($SD=0.03$) after approximately $800$ corrections and then stagnates until all regions are proofread. Both results are very close to the best possible median VI of $0.334$ (calculated by computing maximum overlap with the ground truth). The slope of the trails in Fig.~\ref{fig:ac4trails} shows that guided proofreading requires fewer corrections to reach a reasonable reduction in VI. Fig.~\ref{fig:ac4boxplot} shows the VI distribution across methods.
The results on the L. Cylinder dataset (initial VI $0.379$, $SD=0.118$) are similar. Focused proofreading reduces the median VI to $0.298$ ($SD=0.075$) after $26,170$ corrections ($2,419$ accepted). Guided proofreading reduces the median VI to $0.2996$ ($SD=0.073$) after $27,491$ corrections ($2,696$ accepted).

\paragraph{Automatic selection with threshold.} Focused proofreading was not designed to run automatically. This explains very poor performance on the AC4 subvolume (VI of $1.9$, $SD=0.496$) and on the L. Cylinder dataset (VI of $2.75$, $SD=0.789$). For guided proofreading we define the threshold $p_t=0.95$ for both datasets. This reduces median VI in the AC4 subvolume to $0.398$ ($SD=0.068$). This is an impressive result and comparable to expert performance. Guided proofreading also reduces VI in the L. Cylinder data to $0.352$ ($SD=0.087$).

\paragraph{Merge Error Detection} Guided proofreading performs merge error detection prior to split error detection. The classifier found 10 merge errors in the AC4 subvolume of which 4 reduce VI. Automatic selection with $p_t=0.95$ corrected 6 of these errors (Prec./Recall 0.87/0.80, f1-score 0.80). This was not captured in median VI but resulted in a mean VI reduction from $0.512$ ($SD=0.09$) to $0.509$ ($SD=0.086$). The selection oracle reduced mean VI with only merge errors to $0.508$ ($SD=0.086$). In the forced choice user study, participants marked 1.9 merge errors (experts: 2) merge errors for correction and reduce mean VI to $0.502$ (experts: VI $0.503$, $SD=0.086$). This shows how hard it is to identify merge errors and how little they effect VI. In 50 sections of the L. Cylinder dataset 151 merge errors were automatically found of which 17 reduce VI. Automatic selection with $p_t=0.95$ corrected 6 true VI-reducing errors and 30 VI-increasing ones (Prec./Recall 0.82/0.73, f1-score 0.77) without - in sum - any effect on the VI.

>>>>

We compare guided proofreading and focused proofreading classifiers and report precision and recall as well as f1 scores across datasets.

\paragraph{L.~Cylinder.} Evaluation was performed on previously unseen sections of mouse cortex volume of Kasthuri~\etal~\cite{kasthuri2015saturated}. We generated an unbalanced dataset of 81,184 correct and 8,780 split error patches in respect to the ground truth labeling. We then ranked each patch by using focused proofreading, guided proofreading and compared precision/recall (Table \ref{tab:prcyl}. Our method exhibits higher precision and recall for correct and error patches.

\begin{table}[t]
\caption{Classifier comparison on an unbalanced test set of the L.~Cylinder volume.}%While the training of our classifier is more expensive, testing accuracy is superior. }
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
 & Precision & Recall & F1 score & \# \\ 
\midrule
\emph{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
Correct & 0.93 & 0.31 & 0.47 & 81,184 \\ 
Split error & 0.11 & 0.78 & 0.19 & 8,780 \\ 
\emph{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
Correct & 1.00 & 0.93 & 0.96 & 81,184 \\ 
Split error & 0.61 & 0.96 & 0.74 & 8,780 \\ 
\bottomrule
\end{tabular} 
}
\label{tab:prcyl}
\end{table}

@@

\begin{table}[t]
\caption{Classifier comparison on correct and split error patches of the AC4 subvolume.}%While the training of our classifier is more expensive, testing accuracy is superior. }
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
& Precision & Recall & F1 score & \# \\ 
\midrule
\emph{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
Correct & 0.94 & 0.69 & 0.80 & 3,488 \\ 
Split error & 0.14 & 0.51 & 0.21 & 332 \\ 
\emph{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
correct & 1.00 & 0.92 & 0.96 & 3,488 \\ 
split error & 0.54 & 0.95 & 0.69 & 332 \\ 
\bottomrule
\end{tabular} 
}
\label{tab:prac4}
\end{table}

@@

\paragraph{Selection oracle.} Accepting and rejecting proofreading corrections with the selection oracle yields the best performance on all datasets because all detected merge and split errors are corrected as long as the segmentation is improved. Fig.~\ref{fig:ac4trails} shows slope of VI reduction using the selection oracle on the AC4 subvolume (initial median VI $0.476$, $SD=0.089$). With focused proofreading, the selection oracle reaches a median VI of $0.353$ ($SD=0.037$) after $1605$ corrections. With guided proofreading, the oracle results in a median VI of $0.342$ ($SD=0.03$) after approximately $800$ corrections and then stagnates until all regions are proofread. Both results are very close to the best possible median VI of $0.334$ (calculated by computing maximum overlap with the ground truth). The slope of the trails in Fig.~\ref{fig:ac4trails} shows that guided proofreading requires fewer corrections to reach a reasonable reduction in VI. Fig.~\ref{fig:ac4boxplot} shows the VI distribution across methods.
The results on the L.~Cylinder dataset (initial VI $0.379$, $SD=0.118$) are similar. Focused proofreading reduces the median VI to $0.298$ ($SD=0.075$) after $26,170$ corrections ($2,419$ accepted). Guided proofreading reduces the median VI to $0.2996$ ($SD=0.073$) after $27,491$ corrections ($2,696$ accepted).

\paragraph{Automatic selection with threshold.} Focused proofreading was not designed to run automatically. This explains very poor performance on the AC4 subvolume (VI of $1.9$, $SD=0.496$) and on the L.~Cylinder dataset (VI of $2.75$, $SD=0.789$). For guided proofreading we define the threshold $p_t=0.95$ for both datasets. This reduces median VI in the AC4 subvolume to $0.398$ ($SD=0.068$). This is an impressive result and comparable to expert performance. Guided proofreading also reduces VI in the L.~Cylinder data to $0.352$ ($SD=0.087$).

\paragraph{Merge Error Detection} Guided proofreading performs merge error detection prior to split error detection. The classifier found 10 merge errors in the AC4 subvolume of which 4 reduce VI. Automatic selection with $p_t=0.95$ corrected 6 of these errors (Prec./Recall 0.87/0.80, f1-score 0.80). This was not captured in median VI but resulted in a mean VI reduction from $0.512$ ($SD=0.09$) to $0.509$ ($SD=0.086$). The selection oracle reduced mean VI with only merge errors to $0.508$ ($SD=0.086$). In the forced choice user study, participants marked 1.9 merge errors (experts: 2) merge errors for correction and reduce mean VI to $0.502$ (experts: VI $0.503$, $SD=0.086$). This shows how hard it is to identify merge errors and how little they effect VI. In 50 sections of the L.~Cylinder dataset 151 merge errors were automatically found of which 17 reduce VI. Automatic selection with $p_t=0.95$ corrected 6 true VI-reducing errors and 30 VI-increasing ones (Prec./Recall 0.82/0.73, f1-score 0.77) without - in sum - any effect on the VI.
